---
title: "02 Data Acqusition"
author: "Mohammad Alam"
date: "07-05-2021"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

##Task 1:
Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service. You just have to Google them. You can use whatever service you want. For example, you can get data about your listening history (spotify), get data about flights (skyscanner) or just check the weather forecast. Print the data in a readable format, e.g. a table if you want, you could also plot it. I have added 7 days weather Information of Hamburg.



```{r}

library(jsonlite)
library(glue)
library(RSQLite)
library(httr)
library(xml2)
library(tidyverse)
library(tibble)  
library(readr)     
library(dplyr)    
library(magrittr) 
library(tidyr)    
library(stringr)
library(ggplot2)



resp <- GET('http://www.7timer.info/bin/api.pl?lon=53.55&lat=9.99&product=civillight&output=json')

air_data<- resp %>% 
  .$content %>% 
  rawToChar() %>% 
  fromJSON()
changed_data <- air_data[[3]]
changed_data

```






##Task 2:
Scrape one of the competitor websites of canyon (either https://www.rosebikes.de/ or https://www.radon-bikes.de) and create a small database. The database should contain the model names and prices for at least one category. Use the selectorgadget to get a good understanding of the website structure, it is really helpful. After scraping your data, convert it to a readable format. Prices should be in a numeric format without any other letters or symbols. Also check if the prices are reasonable or not.


```{r}
library(tidyverse) 
library(rvest)     
library(xopen)     
library(jsonlite)  
library(glue)      
library(stringi)   

url_home          <- "https://www.rosebikes.de/fahrr%C3%A4der/mtb/trail-/-enduro"


html_home         <- read_html(url_home) # Read in the HTML for the entire web page


bike_model <- html_home %>% 
  
  html_nodes(css = ".catalog-category-bikes__title-text") %>% 
  html_text() %>%
  
  str_remove_all("\n") 

bike_model

# data scraping 

bike_price_in_euro <- html_home %>%
  
  html_nodes(css = ".catalog-category-bikes__price-title") %>%
  html_text() %>%
  
  str_remove_all("\\.") %>%
  stringr::str_replace_all(pattern = "\nab ", replacement = "") %>%
  stringr::str_replace_all(pattern = "\n", replacement = "") 

bike_price_in_euro

# merging the two tables into one

data_accu <- tibble(bike_model, bike_price_in_euro)

data_accu <- data_accu %>% mutate(bike_price_in_euro = as.character(gsub("???", ",",bike_price_in_euro)))
data_accu$bike_price_in_euro <- as.character(gsub(",","",data_accu$bike_price_in_euro))
data_accu$bike_price_in_euro <- as.character(gsub("ab","",data_accu$bike_price_in_euro))
#d<-da2
data_accu


write_rds(data_accu, "Data_Acquisition_2nd_part.rds")

write.csv(x=data_accu, file="Data_Acquisition_2nd_part.csv")

```